\section{Finite length in characteristic zero}
\label{sec:characteristic-zero}

In this section, we present the first of our two main results, 
which is a method for proving the finite length property assuming that the underlying field has characteristic zero. 
Under this assumption, we will establish the finite length property of the Rado atoms (Example~\ref{ex:rado-graph}) and for the vector atoms (Example~\ref{ex:vector-space-atoms}). 
These are new results. 
We also think that the proof itself, even when applied to get already known results for the equality atoms (Example~\ref{ex:equality-atoms}), is of independent interest and arguably simpler than previously known proofs.
The method that we use will work for all structures satisfying the following condition. 
 
\begin{definition}[Oligomorphic approximation]\label{def:oligomorphic-approximation} 
    We say that a homogeneous structure $\A$ has \emph{oligomorphic approximation} if, 
    for every $d \in \set{1,2,\ldots}$, 
    there exists a family $\Bclass$ of finite substructures of $\A$ such that: 
    \begin{bracketenumerate}
        \item \label{item:oligomorphic-approximation-embedding} 
        every finite substructure $S$ of $\A$ is a substructure of some $\B_S \in \Bclass$; and

        \item \label{item:oligomorphic-approximation-orbits} 
        there is a common finite upper bound, for all $\B \in \Bclass$, on the number of orbits in $\B^d$ with respect to automorphisms of $\B$.
    \end{bracketenumerate}
\end{definition}

This is related to the notion of \emph{smooth approximation} in model theory,
introduced in~\cite[p.~440]{KLM89} and studied in depth in~\cite{CherlinHrushovski_03}.
There one asks for a family $\Bclass$ that does not depend on $d$, 
and instead of (\ref{item:oligomorphic-approximation-orbits}) one requires that: 
\begin{description}
    \item[(2')]
    $\A$ is oligomorphic, and each $\B \in \Bclass$ is homogeneous. 
\end{description}

\begin{theorem}\label{thm:have-oligomorphic-approximation}
    The following structures have oligomorphic approximation: 
    \begin{romanenumerate}
        \item\label{item:smooth-implies-oligomorphic-approximation}   
        any smoothly approximated structure;\footnote{We work over the canonical vocabulary if the structure is not already homogeneous; 
        see \cite[p.~443]{KLM89}. This does not change the automorphism group or, consequently, the finite length property.}
        
        \item\label{item:eq-has-oligomorphic-approximation} 
        the equality atoms from Example~\ref{ex:equality-atoms};
        
        \item\label{item:vec-has-oligomorphic-approximation}
        the vector atoms from Example~\ref{ex:vector-space-atoms}, for any finite field $\innerfield$;        
        
        \item\label{item:rado-has-oligomorphic-approximation} 
        the Rado atoms from Example~\ref{ex:rado-graph}.

    \end{romanenumerate}
\end{theorem}

Before proving this, let us note that the ordered atoms (Example~\ref{ex:order-atoms}) do not have oligomorphic approximation.

\begin{non-example}\label{non-ex:weak-smooth-approximation}
Consider the rational numbers with the usual order. 
The finite substructures in this case are finite total orders, 
and already for dimension $d=1$, a finite total order of size $n$ has $n$ orbits. 
So no family $\Bclass$ satisfies both conditions (\ref{item:oligomorphic-approximation-embedding}) and (\ref{item:oligomorphic-approximation-orbits}).
\lipicsEnd\end{non-example}

\begin{proof}[Proof of Theorem~\ref{thm:have-oligomorphic-approximation}]
    For each of these structures, we exhibit a family $\Bclass$ satisfying the two conditions. In fact, in each case the family will not depend on the parameter $d$.
    \begin{romanenumerate}
        \item
        For a homogeneous structure $\A$ smoothly approximated by $\Bclass$, 
        we just use the family $\Bclass$.
        We only need to check condition~(\ref{item:oligomorphic-approximation-orbits}), so let $\B \in \Bclass$. 
        It is easy to check that, as observed in \cite[(II)]{KLM89}, two tuples in $\B^d$ are in the same orbit if and only if they are in the same orbit of $\A^d$.
        Hence the number of orbits in $\B^d$ is at most that of $\A^d$, which is a finite upper bound because $\A$ is oligomorphic.

        \item 
        For the equality atoms, we can choose $\Bclass$ to be all finite subsets, which clearly satisfies~(\ref{item:oligomorphic-approximation-embedding}). 
        Each of these is homogeneous: we can extend a bijection between subsets to a permutation.
        So $\Bclass$ satisfies~(2') and hence~(\ref{item:oligomorphic-approximation-orbits}) by the above argument.

        \item 
        For the vector atoms, we choose $\Bclass$ to be all subspaces of finite dimension. 
        Each of these is homogeneous since we can, by extending a linearly independent set to a basis, extend linear bijections between subspaces to a linear permutation. 
        Again $\Bclass$ satisfies~(\ref{item:oligomorphic-approximation-embedding}) and~(2') hence~(\ref{item:oligomorphic-approximation-orbits}).
        This argument applies to any finite field $\innerfield$.

        \item 
        The most interesting case is the Rado atoms, which is not smoothly approximated~\cite[Rem.~2.1.2]{CherlinHrushovski_03} (essentially because the finite homogeneous graphs~\cite[p.~100]{Gardiner1976} are not diverse enough). 
        The witness for oligomorphic approximation is a family of \emph{symplectic graphs}: see~\cite[Sec.~8.11]{GR01}.%
        \footnote{We are grateful to Ehud Hrushovski for drawing our attention to this construction.} 
        For every $n \in \set{1,2,\ldots}$ define a finite graph as follows. 
        The set of vertices is the vector space over the two-element field with basis 
        \begin{align*}
            \set{e_1,\ldots,e_n, f_1,\ldots,f_n}.
        \end{align*}
        Since the field has two elements, we can view vertices as subsets of this basis. In this graph, there is an edge between vertices $v$ and $w$ if and only if the sets 
        \begin{align*}
            \setbuild{ i \in \set{1,\ldots,n}}{ $e_i \in v$ and $f_i \in w$ }\\
            \setbuild{ i \in \set{1,\ldots,n}}{ $f_i \in v$ and $e_i \in w$ }
        \end{align*}
        have different sizes modulo two. 
        These graphs (embedded in all possible ways in the Rado graph) satisfy condition~\eqref{item:oligomorphic-approximation-embedding} from Definition~\ref{def:oligomorphic-approximation}, i.e.~every finite graph embeds in some symplectic graph~\cite[Thm.~8.11.2]{GR01}. 
       It is also not difficult to prove condition~\eqref{item:oligomorphic-approximation-orbits}, 
       % removed reference to Appendix B
       i.e.~that the number of orbits of $d$-tuples in symplectic graphs is uniformly bounded by a function of $d$ only. \qedhere
    \end{romanenumerate}
\end{proof}

The main result of this section is the following theorem.

\begin{theorem}\label{thm:weak-smooth-approximation-finite-length}
    If $\A$ has oligomorphic approximation, then it has the finite length property over any field of characteristic $0$.
\end{theorem}

Combining Theorems~\ref{thm:have-oligomorphic-approximation} and~\ref{thm:weak-smooth-approximation-finite-length}, we can get the following results, both old and new, concerning the finite length property.

\begin{corollary}\label{cor:weak-finite-length}
    Over any field of characteristic $0$, the following structures have the finite length property: 
    (\ref{item:smooth-implies-oligomorphic-approximation}) all smoothly approximated structures;
    (\ref{item:eq-has-oligomorphic-approximation}) the equality atoms; 
    (\ref{item:vec-has-oligomorphic-approximation}) the vector atoms; 
    (\ref{item:rado-has-oligomorphic-approximation}) the Rado atoms.
\end{corollary}

As mentioned in the introduction, the finite length property was already known for the equality atoms~---~even over arbitrary fields. 
The results for the vector atoms and the Rado atoms are new. 
The assumption on characteristic zero is important, at least in the case of the vector atoms 
where the finite length property is known to fail over finite fields: see~\cite[Sec.~4.4]{BFKM24}. 
Later on in this paper, we will prove the result for the Rado atoms again using a different method that works for any field.

The rest of this section is devoted to proving Theorem~\ref{thm:weak-smooth-approximation-finite-length}.

\begin{proof}
    [Proof of Theorem~\ref{thm:weak-smooth-approximation-finite-length}]
Fix a structure $\A$ with oligomorphic approximation and a field of characteristic zero. 
Since the field is fixed, we omit the field subscript and write $\Lin X$ for linear combinations of elements in $X$ that use coefficients from that field. 
Fix some power $d \in \set{1,2,\ldots}$. 
Our goal is to show that $\Lin \A^d$ has the finite length property. 
For technical reasons, we apply the assumption on oligomorphic approximation not to $d$, but to $2d$, yielding  some class $\Bclass$ of finite structures that satisfies Definition~\ref{def:oligomorphic-approximation}.

We will now proceed in three steps. 
For convenience, we summarise these steps in Figure~\ref{fig:proof-summary-cogless}. 

\begin{figure}
% https://q.uiver.app/#q=WzAsOSxbMCwwLCJcXHRleHR7bGVuZ3RoIG9mICRcXExpbiBcXEFeZCR9ICJdLFswLDIsIlxcZGlzcGxheXN0eWxlXFxzdXBfe1xcQiBcXGluIFxcQmNsYXNzfSBcXHRleHR7bGVuZ3RoIG9mICRcXExpbiBcXEJeZCR9Il0sWzAsNiwiXFxkaXNwbGF5c3R5bGVcXHN1cF97XFxCIFxcaW4gXFxCY2xhc3N9IFxcdGV4dHtudW1iZXIgb2Ygb3JiaXRzIGluICRcXEJeezJkfSR9Il0sWzEsMSwiXFx0ZXh0eyhMZW1tYX5cXHJlZntsZW06cmVkdWNlLXRvLWZpbml0ZS1zdWJzdHJ1Y3R1cmVzfSl9Il0sWzEsMywiXFx0ZXh0eyhMZW1tYX5cXHJlZntsZW06ZGltLWJvdW5kcy1sZW5ndGh9KX0iXSxbMCw0LCJcXGRpc3BsYXlzdHlsZVxcc3VwX3tcXEIgXFxpbiBcXEJjbGFzc30gXFx0ZXh0e2RpbWVuc2lvbiBvZiB9IFxcbGluZXFmdW57XFxMaW4gXFxCXmR9e1xcTGluIFxcQl5kfSJdLFsxLDUsIlxcdGV4dHsoTGVtbWF+XFxyZWZ7bGVtOmJvdW5kLW9uLWRpbS1mb3ItZmluaXRlLXNldH0pfSJdLFsxLDcsIlxcdGV4dHsoRGVmaW5pdGlvbn5cXHJlZntkZWY6b2xpZ29tb3JwaGljLWFwcHJveGltYXRpb259KX0iXSxbMCw4LCJcXGluZnR5Il0sWzEsMCwiXFxnZXEiLDMseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJub25lIn0sImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNSwxLCJcXGdlcSIsMyx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6Im5vbmUifSwiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFsyLDUsIj0iLDMseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJub25lIn0sImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbOCwyLCI+IiwzLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoibm9uZSJ9LCJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d
\begin{tikzcd}[row sep=tiny]
	{\text{length of $\Lin \A^d$} } & \\
	& {\text{(Lemma~\ref{lem:reduce-to-finite-substructures})}} \\
	{\displaystyle\sup_{\B \in \Bclass} \text{length of $\Lin \B^d$}} \\
	& {\text{(Lemma~\ref{lem:dim-bounds-length})}} \\
	{\displaystyle\sup_{\B \in \Bclass} \text{dimension of } \lineqfun{\Lin \B^d}{\Lin \B^d}} \\
	& {\text{(Lemma~\ref{lem:bound-on-dim-for-finite-set})}} \\
	{\displaystyle\sup_{\B \in \Bclass} \text{number of orbits in $\B^{2d}$}} \\
	& {\text{(Definition~\ref{def:oligomorphic-approximation})}} \\
	\infty
	\arrow["\geq"{marking, allow upside down}, draw=none, from=3-1, to=1-1]
	\arrow["\geq"{marking, allow upside down}, draw=none, from=5-1, to=3-1]
	\arrow["{=}"{marking, allow upside down}, draw=none, from=7-1, to=5-1]
	\arrow["{>}"{marking, allow upside down}, draw=none, from=9-1, to=7-1]
\end{tikzcd}
\caption{
    \label{fig:proof-summary-cogless}
    Summary of the proof of Theorem~\ref{thm:weak-smooth-approximation-finite-length}.}
\end{figure}

    \begin{lemma}\label{lem:reduce-to-finite-substructures}
        For every $d \in \set{1,2,\ldots}$ we have 
        \begin{align*}
        \text{length of }\Lin \A^d
        \quad \leq \quad  \sup_{\B \in \Bclass} \text{\ length of }\Lin \B^d.
        \end{align*}
   %     where the supremum ranges over finite sets of atoms.
    \end{lemma}
    \begin{proof}
        Consider some chain of equivariant subspaces 
        \begin{align*}
            V_0 \subset V_1 \subset \dots \subset V_n \subseteq \Lin \A^d,
        \end{align*}
        where equivariance is with respect to automorphisms of $\A$. 
        For each $i \in \set{1,\ldots,n}$, choose some vector that is in $V_i$ but not in $V_{i-1}$. 
        Let $S$ be the (finite) set of atoms that appear in these chosen vectors, 
        and use~(\ref{item:oligomorphic-approximation-embedding}) to find some $\B \in \Bclass$ that contains all atoms from $S$. 
        Define  
        \begin{align*}
            W_i = V_i \cap \Lin \B^d.
        \end{align*}
        By homogeneity, every automorphism of $\B$ extends to an automorphism of $\A$, 
        and therefore the space $W_i \subseteq \Lin \B^d$ is equivariant with respect to automorphisms of $\B$. 
        The chain of $W_i$'s continues to be strictly growing, 
        since it contains vectors that witness the growth of the original chain. 
        Hence, the new chain forces the length of $\Lin \B^d$ to be at least $n$. 
    \end{proof}


    Thanks to the above lemma, it remains to show that the length of $\Lin \B^d$ is bounded by some number that depends only on $d$. 
    In our proof, this bound will be the number of orbits in $\B^{2d}$. 
    What we have gained by moving from $\A$ to $\B \in \Bclass$ is that our vector spaces now have finite (albeit unbounded) linear dimension, 
    and are acted upon by finite (albeit unbounded) groups. 
    This will let us leverage a well-known result from representation theory called Maschke's Theorem (see e.g.~\cite[Thm.~6.3]{RepTheoryTextbook}).
    In order to be more precise, recall that we write $V = V_1 \oplus V_2$ if each $v \in V$ is equal to $v_1 + v_2$ for some unique $(v_1, v_2) \in V_1 \times V_2$.

    \begin{fact}[Maschke's Theorem]
        Let $V$ be a finite-dimensional vector space over a field of characteristic zero, equipped with a linear action of a finite group $G$. 
        Then $V$ can be decomposed as 
        \begin{align*}
            V = V_1 \oplus \cdots \oplus V_n, % Slight abuse of notation: external vs internal
        \end{align*}
        where each $V_i$ is an equivariant subspace (with respect to the action of $G$) 
        that has length $1$, 
        i.e.~the only equivariant subspaces of $V_i$ are the zero space and the full space $V_i$.
    \end{fact}


    We will use this theorem to bound the lengths of the vector  spaces $\Lin \B^d$ for $\B \in \Bclass$. 
    For two vector spaces $V$ and $W$ equipped with a linear action of the same group $G$, let us write 
    \[
        \lineqfun{V}{W} = 
        \left\{
            \psi : V \to W
            \ \middle\vert\
            \text{ $\psi$ is linear and }
            \forall g \in G, \forall v \in V : g(\psi(v)) = \psi(g(v))\
        \right\}
    \]
    for the set of all those linear maps from $V$ to $W$ that are equivariant with respect to the action of $G$. 
   This set is closed under taking linear combinations, and therefore it can be seen as a vector space. 
    In particular, it is meaningful to talk about the dimension of this space. 
    \begin{lemma}\label{lem:dim-bounds-length}
        Let $V$ be a finite-dimensional vector space over a field of characteristic zero, 
        equipped with a linear action of a finite group $G$. 
        Then 
        \begin{align*}
            \text{length of\, $V$} 
            \quad \leq \quad 
            \text{dimension of } \lineqfun{V}{V}.
        \end{align*}
    \end{lemma}
    \begin{proof}
        Apply Maschke's Theorem, yielding a decomposition 
        \begin{align*}
        V = V_1 \oplus \cdots \oplus V_n,
        \end{align*}
        where the subspaces $V_1,\ldots,V_n$ are equivariant and of length $1$, with respect to the action of the group $G$. 
        The length is additive with respect to direct sums (see e.g.~\cite[Prop.~3.17]{RepTheoryTextbook}), i.e.
        \begin{align*}
            \text{length of $V$} 
            = \text{length of $V_1$} + \cdots + \text{length of $V_n$},
        \end{align*}
        so the length of $V$ is equal to $n$. 
        
        We will now consider the right-hand side of the inequality in the statement of the lemma.
        For every $i \in \set{1,\ldots,n}$, there is an equivariant linear map from $V$ to itself that 
        \begin{itemize}
            \item is the identity on $V_i$; and
            \item maps vectors from the other components to zero.
        \end{itemize}
        This gives us at least $n$ equivariant linear maps from $V$ to itself. 
        None of these maps can be spanned by the others, 
        and hence the dimension is no less than $n$. 
    \end{proof}

    Thanks to Lemmas~\ref{lem:reduce-to-finite-substructures} and~\ref{lem:dim-bounds-length}, 
    the length of the vector space $\Lin \A^d$ is bounded by the dimensions of the vector spaces
    \begin{align}\label{eq:endo-maps-b-d}
        \lineqfun{ \Lin \B^d}{\Lin \B^d}, 
        \tag{$*$}
    \end{align}
    where $\B$ ranges over the family $\Bclass$.
    To complete the proof of the theorem, it still remains to show that these dimensions are bounded by some number that depends only on $d$.
    We do so now.

    \begin{lemma}\label{lem:bound-on-dim-for-finite-set} 
        For every $\B \in \Bclass$, 
        the dimension of the vector space in~\eqref{eq:endo-maps-b-d} is 
        precisely the number of orbits in $\B^{2d}$.
    \end{lemma}
    \begin{proof}
        A linear map $\psi$ in the $\FF$-vector space~\eqref{eq:endo-maps-b-d} can be seen as a square matrix indexed by $\B^d$, 
        i.e.~a function
        \begin{align*}
            {\B^d \times \B^d} \to \field ; 
            \quad
            \text{defined by } (x, y) \mapsto \lambda_{x,y} \text{ where } \psi(1 \cdot x) = \sum_{z} \lambda_{x,z} \cdot z.
        \end{align*}
        This function must be equivariant with respect to automorphisms of $\B$, 
        i.e.~for any automorphism $g$ and $x, y \in \B^d$ we must have $\lambda_{g(x),g(y)} = \lambda_{x, y}$.
        So to define such a function, we need to choose one element of $\field$ for each orbit of the $\B^d \times \B^d$. 
        The dimension of the space in~\eqref{eq:endo-maps-b-d} is therefore equal to the number of orbits of $\B^{2d}$.
    \end{proof}
This number of orbits has a finite upper bound that depends only on $d$, by condition~(\ref{item:oligomorphic-approximation-orbits}) of Definition~\ref{def:oligomorphic-approximation}. 
This completes the proof of Theorem~\ref{thm:weak-smooth-approximation-finite-length}.
\end{proof}

The inequalities shown in Figure~\ref{fig:proof-summary-cogless} give us upper bounds on the length of $\Lin \A^d$. 
In the case of the equality atoms, this bound is the $2d$-th Bell number. 
In the case of the vector atoms from Example~\ref{ex:vector-space-atoms}, the bound is the number of linear dependency patterns for $2d$-tuples over a finite field. 
Such a pattern is described by: 
(a)~indicating a subset of the coordinates which is a basis for the tuple; 
and (b)~indicating the basis decompositions for the remaining coordinates. 
This can be done in at most $2^{(2d)^2}$ ways.
%In Appendix~\ref{sec:appendix-symplectic} we give a similar upper bound in the case of the Rado atoms, 
%also super-exponential in $d$.
A similar upper bound, also super-exponential in $d$, can be obtained for the Rado graph by an analysis of orbits in symplectic graphs.
